quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-10-22 paper-quollr.Rmd
Added Figure 1 title

```{r overviewhtml, eval=knitr::is_html_output(), fig.cap="algorithm", fig.pos='H', layout = "l-page"}

@@

The source code for reproducing this paper can be found at: [https://github.com/JayaniLakshika/paper-quollr](https://github.com/JayaniLakshika/paper-quollr).

This article is created using \CRANpkg{knitr} [@yihui2015] and \CRANpkg{rmarkdown} [@yihui2018] in R with the `rjtools::rjournal_article` template. These `R` packages were used for this work: `cli` [@gabor2025], `dplyr` [@hadley2023], `ggplot2` [@hadley2016], `interp` (>= 1.1-6) [@albrecht2024], `langevitour` [@paul2023], `proxy`[@david2022], `stats` [@core2025], `tibble` [@kirill2023], `tidyselect` [@lionel2024], `crosstalk` [@joe2023], `plotly` [@chapman2020], `htmltools` [@joe2024], `kableExtra` [@hao2024], `patchwork` [@thomas2024], and `readr` [@hadley2024].

>>>>

```{r overviewhtml, eval=knitr::is_html_output(), fig.cap="Wireframe model representation of the NLDR layout, lifted and displayed in high-dimensional space. The left panel shows the NLDR layout with a triangular mesh overlay, forming the wireframe structure. This mesh can be lifted into higher dimensions and projected to examine how the geometric structure of the data is preserved. Panels (a1–a4) display different \\twoD projections of the lifted wireframe, where the underlying curved sheet structure of the data is more clearly visible. The triangulated mesh highlights how local neighborhoods in the layout correspond to relationships in the high-dimensional space, enabling diagnostics of distortion and preservation across dimensions.", fig.pos='H', layout = "l-page"}

@@

The source code for reproducing this paper can be found at: [https://github.com/JayaniLakshika/paper-quollr](https://github.com/JayaniLakshika/paper-quollr). This article is created using \CRANpkg{knitr} [@yihui2015] and \CRANpkg{rmarkdown} [@yihui2018] in R with the `rjtools::rjournal_article` template. These `R` packages were used for this work: `cli` [@gabor2025], `dplyr` [@hadley2023], `ggplot2` [@hadley2016], `interp` (>= 1.1-6) [@albrecht2024], `langevitour` [@paul2023], `proxy`[@david2022], `stats` [@core2025], `tibble` [@kirill2023], `tidyselect` [@lionel2024], `crosstalk` [@joe2023], `plotly` [@chapman2020], `htmltools` [@joe2024], `kableExtra` [@hao2024], `patchwork` [@thomas2024], and `readr` [@hadley2024].
